Solution-aware vs global ReLU selection: \\ partial MILP strikes back for DNN verification

### 2025-04-25 ATVA 2025/proofsb.tex
samll update

We provide in Table \ref{table112} the average as well as maximum time to perform $MILP_X$ calls as called by pMILP, on a given input: image 3 for MNIST, and image 76 for CIFAR10. 
For 6x500, we provide results for two different $\varepsilon$, following our test from Figure \ref{fig2}.

>>>>

We provide in Table \ref{table112} the average as well as maximum time to perform $\MILP_X$ calls as called by pMILP, on a given input: image 3 for MNIST, and image 76 for CIFAR10. 
For 6x500, we provide results for two different $\varepsilon$.

%, following our test from Figure \ref{fig2}.
